% !TEX program = pdflatex
% Cover Letter — for IJPM submission

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{left=2cm, right=2cm, top=2cm, bottom=2cm}
\usepackage{newtxtext}
\usepackage{hyperref}
\usepackage{setspace}
\onehalfspacing
\usepackage{parskip}
\setlength{\parskip}{0.8em}

\pagestyle{empty}

\begin{document}

Dear Professor Martina Huemann,

We are pleased to submit our manuscript, ``\textbf{\textit{How digital communication tool use shapes improvisation capability in large-scale projects through meta-knowledge: Distributed cognition perspective}},'' for consideration for publication in the \textit{International Journal of Project Management}.

Large-scale construction projects routinely encounter unexpected contingencies that demand rapid, creative responses---precisely the conditions under which improvisation capability becomes critical. Despite growing reliance on digital communication tools (DCTs) for cross-organizational coordination, it remains unclear how DCT use translates into team improvisation capability and through what cognitive mechanisms this process operates. Drawing on distributed cognition theory, this study develops and tests a model in which work-oriented and social-oriented DCT use shape improvisation capability through three dimensions of meta-knowledge: structural, relational, and procedural. Using three-wave time-lagged survey data from 255 large-scale construction project teams in China, we address the following two research questions:

\textbf{RQ1:} \textit{How do work-oriented and social-oriented digital communication tool use influence improvisation capability in large-scale construction project teams?}

\textbf{RQ2:} \textit{Does project teams' meta-knowledge mediate the relationship between digital communication tool use and improvisation capability?}

Our contribution aligns closely with IJPM's aims and scope in three ways:

\textbf{1. Direct relevance to project organizing and digital transformation}

This study addresses a gap at the intersection of digital collaboration and project team improvisation capability, showing that DCTs function not merely as communication channels but as cognitive infrastructure-building systems. As shown in Table 1 of the manuscript, existing research on antecedents of improvisation in project management has concentrated on cognitive and psychological states, knowledge and experience bases, and contextual triggers, while the role of communication technology remains largely unexamined. This study fills that gap by demonstrating how digital tools actively reshape team organizing in temporary, cross-organizational project settings, a topic of growing importance as construction and infrastructure projects become increasingly digitalized. The findings directly respond to IJPM's interest in project-based organizations and technology-enabled project management.

\textbf{2. Theoretical advancement through distributed cognition and meta-knowledge}

The study makes two interconnected theoretical contributions. First, it introduces a three-dimensional meta-knowledge framework---structural (who knows what), relational (who knows whom), and procedural (how to access and mobilize knowledge)---into project management research, where the concept has been largely absent despite its theoretical relevance to coordination in temporary organizations. The findings demonstrate that structural, relational, and procedural meta-knowledge each play distinct roles in shaping improvisation capability, revealing that meta-knowledge is not a monolithic cognitive resource but a multifaceted structure whose dimensions connect to team capability through differentiated pathways. Second, by extending distributed cognition theory to digitally mediated project environments, this study shows that team improvisation capability depends not only on knowledge possession but equally on the ability to locate, combine, and mobilize distributed knowledge under time pressure. This challenges the prevailing assumption in project management research that knowledge acquisition and expertise are the primary drivers of team performance, and positions meta-knowledge development as a critical cognitive foundation for improvisation in complex project settings.

\textbf{3. Actionable practical guidance for project managers}

The study translates its theoretical findings into concrete recommendations for designing digitally mediated project environments. It shows that immediacy and creativity follow distinct meta-knowledge pathways, enabling project managers to conduct differentiated capability assessments aligned with project type and lifecycle phase. It further proposes a distributed cognition system architecture---comprising expert capability atlases, collaboration network dashboards, and procedure knowledge bases---that maps directly onto the three meta-knowledge dimensions. This architecture, visualized in Figure 4 of the manuscript, provides practitioners with a concrete blueprint for building meta-knowledge-oriented digital workspaces implementable through modern platforms such as DingTalk, Feishu, and Microsoft Teams.

We believe this work is timely and relevant to IJPM's readership. The manuscript is not under review elsewhere, has been approved by all co-authors, and presents no conflicts of interest.

Thank you very much for considering our work. We look forward to your feedback.

Yours sincerely,

Xueqing Gan (Corresponding Author)\\
School of Business, Jiangsu University of Science and Technology\\
Zhenjiang 212100, China\\
Email: xueq\_gan@163.com

\end{document}
