\section{Literature review and theoretical foundation}
\label{sec:literature}

Three streams of literature are related to our research questions: (1) works on sustainable competitive advantage, (2) CEM literature regarding competitive advantage, (3) CEM literature on organizational resilience. This section reviews these studies to build our theoretical foundation. First, we synthesized the evolution of sustainable competitive advantage research to propose the "Resource-Environment-Strategy" framework as our research framework. Second, we reviewed extant CEM literature regarding competitive advantage to contextualize this framework and identified nine potential antecedents. Third, we reviewed organizational resilience studies to further clarify its relationship with sustainable competitive advantage.

\subsection{"Resource-Environment-Strategy" framework from sustainable competitive advantage studies}

We derived the "Resource-Environment-Strategy" framework from a review of the literature on sustainable competitive advantage. Distinct from conventional competitive advantage, sustainable competitive advantage emphasizes the \textit{durability} of superior performance and the \textit{inimitability} of value-creating capabilities against competitive duplication \citep{oliver1997Sustainable,lado1992CompetencyBased}. Scholars have progressively investigated the antecedents from resource, environment, and strategy perspectives, as shown in Table 1.

The theoretical discourse on sustainable competitive advantage originates from the resource-based view, which posits that the heterogeneous resources are the primary source of advantage \citep{abdeen2025Strategic,zaman2025How}. However, the literature quickly evolved from focusing on tangible assets to more complex resource forms. For instance, \citet{hall1993FRAMEWORK} argued that sustainable advantage is derived primarily from intangible resources—such as reputation and employee know-how—because their causal ambiguity creates formidable barriers to imitation. Further, \citet{black1994Strategic} critiqued the atomistic view of resources, introducing the concept of "resource networks". They posited that advantage arises not from isolated factors but from the complex configuration and complementary relationships between resources.

Building upon the resource-based view, several studies integrating institutional theory and market perspectives argues that resources cannot exist in a vacuum; rather, their value is contingent upon the external environment. \citet{oliver1997Sustainable} provided a seminal integration, demonstrating that a enterprise's advantage is shaped by the interaction between internal resources and external institutional pressures, where social legitimacy becomes a prerequisite for survival. Also, \citet{adner2006Demandbased} introduced a demand-side perspective, arguing that the sustainability of advantage is determined by market heterogeneity and consumer marginal utility rather than supply-side capabilities alone. Empirical work by \citet{mady2024Nexus} further confirms that external drivers, such as regulatory pressure and eco-friendly product demand, are critical forces that compel enterprises to adapt their resource base.

Also, the scholarship also highlights that alignment between resources and the environment requires clear strategic orientation. Strategic orientation reflects the firm's proactive intent and the specific logic it employs to create and capture value \citep{sabug2020Competitive}. \citet{lado1992CompetencyBased} were among the first to propose a comprehensive model that prioritizes "managerial competencies" and "strategic focus". They argued that strategy acts as the engine that transforms input resources into competitive outputs, integrating environmental determinism with strategic choice. This view is supported by \citet{johannessen2003Knowledge}, who highlighted that sustainable competitive advantage is the result of conscious "strategic training" and management intervention. Moreover, \citet{malik2023Strategic} empirically demonstrated that strategic orientations act as essential mediators that leverage technological readiness to achieve sustainable competitive advantage, particularly in emerging markets.

While the literature has identified these three dimensions, prior studies have predominantly examined them in isolation or through linear "net-effect" models. \citet{rouse1999Rethinking} and \citet{levitas2002Rethinking} have debated the difficulties of isolating sources of advantage, pointing to a "black box" in understanding how these factors interact holistically. Current research on sustainable competitive advantage lacks a systematic analysis of how these three dimensions "fit" together. Therefore, this study proposes the "Resource-Environment-Strategy" framework to investigate the configurations of sustainable competitive advantage.

\subsection{Antecedents of sustainable competitive advantage in construction enterprises under "Resource-Environment-Strategy" framework}

Construction enterprises operate as complex, open systems characterized by project discontinuity, fragmented supply chains, and high sensitivity to institutional pressures \citep{ning2022How,wang2026Dynamic}. These distinctive industry attributes render the "Resource-Environment-Strategy" framework pertinent for unraveling the causal complexity underlying the formation of sustainable competitive advantage. This section grounds the "Resource-Environment-Strategy" framework in the body of CEM literature regarding conventional competitive advantage. We selected nine antecedents across the three dimensions as follows.

\subsubsection{Organizational resource and sustainable competitive advantage}

Regarding organizational resource, the CEM literature regarding conventional competitive advantage has witnessed a theoretical evolution from resource-based view to dynamic capabilities view \citep{choi2018Dynamic}. Resource-based view primarily centers on the accumulation of internal resources that are valuable, rare, inimitable, and non-substitutable \citep{barney2021Emergence,jugdev2019Mediated}; rather, dynamic capabilities are formally defined as the potential to "integrate, build, and reconfigure internal and external competences to address rapidly changing environments" \citep{whang2024Understanding}. Situated within these two theoretical lenses, this study identifies \textit{cost stickiness}, \textit{organizational size}, \textit{ESG}, and \textit{digital transformation} as four critical resource-related antecedents.

\textbf{Cost stickiness.} Cost Stickness refers to the asymmetry where costs increase more rapidly with rising activity volume than they decrease during declines. In the project-based construction enterprises, cost stickiness reflects the deliberate retention of slack resources——such as skilled project managers and specialized technical equipment \citep{potgieter2016Maximizing}, acting as a resource investment from a long-term perspective \cite{luo2019Impacts}. Cost stickness enables construction enterprises to rapidly mobilize resources and stimulate innovation when new project opportunities emerge \citep{love2004Industrycentric}, which is specifically required for sustainable competitive advantage.

\textbf{Enterprise size.} Firm size functions as a critical indicator of resource endowment \citep{shao2025Competitive}. Large-scale enterprises typically possess abundant slack resources and lower financing costs, which provide a buffer against the high risks inherent in construction projects. Furthermore, consistent with \citet{maury2018Sustainable} who found that market share significantly predict profit persistence, large construction enterprises benefit from deep social embeddedness \citep{lello2024Professional}. Thus, size determines the type of long-term resource advantages——stability versus flexibility——available to enterprises.

\textbf{Environmental, Social, and Governance (ESG).} ESG performance recently represents a critical intangible resource that transforms ethical behavior and sustainable practices into strategic assets \citep{wang2023Exploring}. Given that construction projects possess significant environmental footprints and social implications, superior ESG performance goes beyond mere compliance to become a mechanism for building trust and legitimacy. For construction enterprises, proactive ESG practices --- ranging from utilizing eco-friendly materials (environmental) and ensuring site safety (social) to maintaining transparent management (governance) --- can reduce friction with stakeholders and enhance corporate reputation \citep{hassan2016Organizational,locatelli2025Social}. As noted by \citet{mattera2022Sustainable}, a strong commitment to sustainable business models, as reflected in high ESG ratings, contributes to a firm's ability to overcome crises and improve long-term financial performance.

\textbf{Digital transformation.} Digital transformation represents a "transformation-based competency" that fundamentally reconfigures a construction enterprise's operational resources \citep{wen2025Gap}. It involves integrating digital technologies (e.g., BIM, IoT) into project lifecycles to enhance decision-making and efficiency \citep{simard2025Project}. \citet{probojakti2025Driving} found that digital transformation significantly improves organizational agility and resiliency, which are pivotal for sustaining competitive edges. Also, \citet{van2025Enhancing} emphasized that data-driven decision-making enabled by digital integration boosts organizational creativity and competitive advantage. Digital transformation allows construction enterprises to better sense environmental changes and seize new market opportunities, thereby securing a sustainable position.

\subsubsection{External environment and sustainable competitive advantage}

Construction enterprises operate as complex open systems where the sustainability of advantage is determined by how well internal capabilities align with external legitimacy requirements and market demands \citep{aghimien2023Dynamic,zhao2024Using}. Recent CEM studies suggested that the external environment is no longer static but characterized by rapid technological disruptions and fluctuating resource availability \citep{ning2022How}. Consequently, to capture the multidimensional nature of these external pressures and opportunities, this study identifies \textit{environmental dynamism} and \textit{environmental munificence} as the two critical environmental antecedents.

\textbf{Environmental dynamism.} Environmental dynamism refers to the rate and unpredictability of change in a firm's external environment, characterized by technological shifts, fluctuating market demands, and evolving regulations \citep{dess1984Dimensions}. In the construction industry, dynamism is currently driven by the "Fourth Industrial Revolution" and increasingly stringent sustainability mandates \citep{aghimien2023Dynamic}. High dynamism challenges the traditional static model of competitive advantage, as existing competencies can rapidly become obsolete. \citet{zhao2024Using} argue that in such transient competitive environments, advantages are easily eroded, compelling firms to continuously sense and seize new opportunities. Therefore, dynamism acts as a stressor that shifts from efficiency-based strategies to flexibility-based dynamic capabilities \citep{ning2022How}.

\textbf{Environmental munificence.} Environmental munificence describes the extent to which an environment can support sustained growth, reflecting the abundance of critical resources and market opportunities \citep{chen2017Munificence}. For construction enterprises, this manifests as the availability of infrastructure projects, financial capital, and collaborative network support \citep{ma2018Unraveling}. A munificent environment provides necessary "slack resources," allowing firms to experiment with innovations and absorb failures without threatening survival. \citet{wang2024Strategic} suggest that firms in munificent environments can leverage diversified operations to capture emerging opportunities. Thus, environmental munificence dictates the "room for maneuver" \citep{whang2024Understanding}.

\subsubsection{Strategic orientation and sustainable competitive advantage}

While \citet{porter1997COMPETITIVE}'s generic strategies have long served as a baseline, recent CEM literature suggested that sustainable competitive advantage emerges not from a single strategic posture but from the dynamic configuration of multiple orientations that match the firm's resource endowment with environmental demands \citep{shao2025Competitive}. To capture the diverse pathways through which construction enterprises position themselves, this study identifies \textit{diversification}, \textit{differentiation}, and \textit{cost leadership} as the three critical strategic antecedents.

\textbf{Diversification.} Diversification refers to the strategic expansion into new market segments or business lines to spread risks and capture emerging opportunities. For construction enterprises facing cyclical demand and intense local competition, diversification is a vital mechanism for survival and growth. \citet{wang2024Strategic} argued that "strategic resource amalgamation" is the driver of diversified operations, enabling contractors to leverage their operational and innovation capabilities across broader markets. Thus, diversification represents a strategy of scope, allowing firms to exploit their existing resource base in novel environmental contexts to sustain competitive advantages \citep{whang2024Understanding}.

\textbf{Differentiation.} Differentiation involves creating a unique value proposition, thereby allowing for premium pricing or customer loyalty. In the construction industry, differentiation is increasingly driven by "soft power" attributes such as corporate image, technical innovation, and brand reputation \citep{anjomshoa2024Key}. \citet{budayan2014Alignment} classified this into "quality and image-related differentiation," emphasizing that firms must align their project management processes with these strategic goals. Furthermore, differentiation is often achieved through the superior implementation of technologies like BIM. \citet{shao2025Competitive} found that image-oriented and quality-oriented competitive strategies are heavily emphasized by contractors to signal competence and secure legitimacy. Consequently, differentiation serves as a strategy of value, insulating firms from direct price competition.

\textbf{Cost Leadership.} Cost leadership is characterized by the pursuit of the lowest operational costs to offer competitive pricing in bidding processes. While often viewed as a traditional strategic orientation, modern cost leadership transcends mere cost-cutting; it involves the rigorous pursuit of efficiency through lean management and technological integration \citep{li2024Lean}. \citet{sabug2020Competitive} highlighted that in competitive markets (e.g., rail sectors), a hybrid approach combining cost leadership with other strategies is often required for success. Thus, cost leadership represents a strategy of efficiency, essential for maintaining the economic viability of projects in the low-margin construction industry \citep{li2025Impact}.

\subsection{Organizational resilience and its relationship with sustainable competitive advantage}

Organizational resilience addresses the fundamental capacity of construction enterprises to survive and thrive amidst contingencies \citep{zhang2022Organizational}. In the CEM literature, organizational resilience is defined as the dynamic capability of an enterprise to anticipate, absorb, recover from, and adapt to unexpected disruptions and shocks \citep{zhang2024Deconstructing}. The relevance of organizational resilience in the construction industry stems from the inherent complexity and uncertainty of project delivery \citep{yao2025Clear}. Construction enterprises frequently face high-impact, low-probability events—ranging from supply chain ruptures to sudden policy shifts—that threaten their viability \citep{wang2026Dynamic}. Unlike traditional risk management, which focuses on identifying specific risks, resilience emphasizes a generalized capacity to cope with the "unknown unknowns" \citep{lv2024Digital}.

Sustainable competitive advantage and organizational resilience represent two distinct yet complementary dimensions of construction enterprises' long-term viability. Sustainable competitive advantage focuses on \textit{market superiority}: it emphasizes the capacity to outperform competitors and secure persistent economic returns, largely under normal market conditions \citep{adner2006Demandbased, betts1994Sustainablea}. In contrast, organizational resilience focuses on \textit{operational robustness}: it emphasizes the capacity to withstand shocks, absorb disruptions, and recover functions during crises or high-uncertainty events \citep{zhang2022Organizational,yao2025Clear}. While sustainable competitive advantage answers the question of "how to thrive and lead," organizational resilience answers "how to survive and persist". 

Studies on competitive advantage rarely account for how high-performance configurations work under crisis. It remains unclear whether the pathways leading to sustainable competitive advantage naturally encompass the attributes required for resilience, or if they leave enterprises vulnerable to disruptions.